### 2015-07-20 analysis/e5_analysis.Rmd
analysis tweaks

for (f in files) {
  jf <- paste("production-results/e5/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answer$scale,
                   degree = jd$answer$degree,
                   stars = jd$answer$manipulation_level,
                   judgment = as.numeric(jd$answer$judgment),
                   language = jd$answer$language)
  d.raw <- bind_rows(d.raw, id)
}
```

@@

# Different take on speaker.p
ma <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(speaker.p = mean( ifelse( (judgment >= 4), 1, 0)))
write.csv(ma, "models/e5a.csv", row.names=FALSE)

>>>>

for (f in files) {
  jf <- paste("production-results/e5/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answer$scale,
                   degree = jd$answer$degree,
                   stars = jd$answer$manipulation_level,
                   judgment = as.numeric(jd$answer$judgment),
                   language = jd$answer$language)
  d.raw <- bind_rows(d.raw, id)
}

# Number of participants
length(unique(d.raw$workerid))
```

@@

#### Different take on speaker.p ###
ma <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(speaker.p = sum( ifelse( (judgment >= 4), 1, 0)))
  #summarise(speaker.p = sum( ifelse( (judgment == 5), stars, 0)))
write.csv(ma, "models/e5a.csv", row.names=FALSE)

table(ma$stars, ma$judgment, ma$degree) / sum(table(ma$stars, ma$judgment))
mn <- filter(ma, scale == "good_excellent", degree=="hi")
nt = table(mn$star, mn$judgment)
nt = nt / sum(nt)

mz <- filter(mz, scale == "good_excellent", degree=="low")
nz = table(mz$star, mz$judgment)

t = nz - nt

t = matrix(table(d$judgment, d$degree), ncol=2, nrow = 5)
p = t[,1] - t[,2]
qplot(c(1, 2, 3, 4, 5), ma$speaker.p)
